oscar_figures

### 2021-03-14 oscar_figures.Rmd
removed pointless line of code

tg_rnaseq_df <- bind_rows(specific_rt, random_hexamer) %>%
  group_by(sample_name) %>%
  mutate(n_healthy = ifelse(risk == "Non-Risk", n, 0)) %>%
  mutate(combined_healthy = sum(n_healthy)) %>%
  select(-n_healthy) %>%
  mutate(combined = sum(n)) %>%
  group_by(sample_name, risk) %>%
  mutate(combined_n = sum(n)) %>%
  ungroup() %>%
  select(-n) %>%
  unique() %>%
  group_by(sample_name) %>%
  mutate(p_value = pbinom(combined_healthy, sum(combined_n), 0.5)) %>%  # single-tailed bionomial test
  mutate(colour = ifelse(risk == "Non-Risk", "lightblue", "red")) %>%
  ungroup() %>%
  mutate(sample_name_ordered = fct_reorder(sample_name, dplyr::desc(combined_n)))

>>>>

tg_rnaseq_df <- bind_rows(specific_rt, random_hexamer) %>%
  group_by(sample_name) %>%
  mutate(n_healthy = ifelse(risk == "Non-Risk", n, 0)) %>%
  mutate(combined_healthy = sum(n_healthy)) %>%
  select(-n_healthy) %>%
  mutate(combined = sum(n)) %>%
  group_by(sample_name, risk) %>%
  mutate(combined_n = sum(n)) %>%
  ungroup() %>%
  select(-n) %>%
  unique() %>%
  group_by(sample_name) %>%
  mutate(p_value = pbinom(combined_healthy, sum(combined_n), 0.5)) %>%  # single-tailed bionomial test
  ungroup() %>%
  mutate(sample_name_ordered = fct_reorder(sample_name, dplyr::desc(combined_n)))
